---
title: "Prueba"
format: dashboard
#orientation: columns
---

```{r}
library(formattable)
library(tidyverse)
```

```{r}

df <- data.frame(
  id = 1:10,
  name = c("Bob", "Ashley", "James", "David", "Jenny",
    "Hans", "Leo", "John", "Emily", "Lee"),
  age = c(28, 27, 30, 28, 29, 29, 27, 27, 31, 30),
  grade = c("C", "A", "A", "C", "B", "B", "B", "A", "C", "C"),
  test1_score = c(8.9, 9.5, 9.6, 8.9, 9.1, 9.3, 9.3, 9.9, 8.5, 8.6),
  test2_score = c(9.1, 9.1, 9.2, 9.1, 8.9, 8.5, 9.2, 9.3, 9.1, 8.8),
  final_score = c(9, 9.3, 9.4, 9, 9, 8.9, 9.25, 9.6, 8.8, 8.7),
  registered = c(TRUE, FALSE, TRUE, FALSE, TRUE, TRUE, TRUE, FALSE, FALSE, FALSE),
  stringsAsFactors = FALSE)

tabla_formateada <- formattable(df, list(
  age = color_tile("white", "orange"),
  grade = formatter("span", style = x ~ ifelse(x == "A",
    style(color = "green", font.weight = "bold"), NA)),
  area(col = c(test1_score, test2_score)) ~ normalize_bar("pink", 0.2),
  final_score = formatter("span",
    style = x ~ style(color = ifelse(rank(-x) <= 3, "green", "gray")),
    x ~ sprintf("%.2f (rank: %02d)", x, rank(-x))),
  registered = formatter("span",
    style = x ~ style(color = ifelse(x, "green", "red")),
    x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes", "No")))
))
```

```{r}

df <- data.frame(
  Product = c("A", "B", "C", "D"),
  Sales = c(1250, 890, 2100, 1500),
  Profit = c(0.12, -0.05, 0.25, 0.08)
)

# Apply formatting to the data frame
tabla_2 <- formattable(df, align = c("l", "r", "r"),
  list(
    # Format the 'Sales' column with commas and a color bar
    Sales = color_bar("lightgreen"),
    # Format the 'Profit' column with percentages and color text based on value
    Profit = formatter("span", 
      style = x ~ style(color = ifelse(x < 0, "red", "darkgreen")),
      x ~ percent(x, digits = 1)
    )
  )
)

```

# Home

## Row 1 {height=75%}
```{r}
tabla_formateada
```

```{r}
tabla_2
```

## Row 3
Formatted table with the following visualizations:

Ages are rendered in gradient.
All A grades are displayed in green bold.
test1_score and test2_score are indicated by horizontal bars and are background-colorized: white (low score) to pink (high score)
final_score shows score and ranking. Top 3 are green, and others are gray.
registered texts are transformed to an icon and yes/no text.

# Tablas para descargar

```{r}

htmltools::browsable(
  tagList(
    reactable(gapminder,
              elementId = "gapminder-table",
              searchable = T,
              filterable = T),
    
    tags$button("Download as CSV", 
                onclick = 
                  "Reactable.downloadDataCSV('gapminder-table')")
  )
) 

```



